CDSR Human Data/Modelling Paper

### 2013-09-12 code/scenarios/cdsr/trunk/papers/ACS2013/main.tex
jk new section 4

Recall from section \ref{} that in addition to being able to represent these regions for a single environment, the cognitive system (1) must recognize regions of the same type in new environments with new contexts, and (2) use the region for multiple reasoning tasks.  While spatial reasoning has been an active topic in AI and robotics for decades, CDSRs present a new problem which requires solutions beyond the current state-of-the-art. Regions are central to QSR work~\cite{Cohn:2001}. Regions can either have crisp boundaries, usually defined by geometric shapes (e.g. the bounding boxes of visually tracked objects~\cite{SridharCohn:10}), or vague boundaries created qualitatively by multiple crisp regions (e.g. the `egg-yolk model'~\cite{Cohn96b}), or by thresholding an underlying spatially-mapped function (e.g. those created by potential fields~\cite{brenneretal07ijcai} or by Gaussian kernels~\cite{burbridge-dearden12}). The fundamental decision when creating a computational model of a CDSR is the method used to represent its boundary. Given their context-dependent nature, boundary definitions based purely on single geometric shapes or a fixed number of points, seem unlikely to model the regions with sufficient accuracy.

However, arbitrary boundaries can be defined using a sequence of geometric primitives (usually straight lines), as in chain codes for image region representations~\cite{Freeman:1961}. This is an approach we followed in previous work \cite{Hawes:2012}, where we defined CDSRs using \textit{anchor points} \cite{DBLP:journals/jetai/KlenkFTK11} as the vertices of the region polygon thereby linking the conceptual regions to perceived objects.   While satisfying the requirements of a cognitive systems solution, applying this model to our results of our experiemnt illustrates two limitations.  First, Regions are not always physically bounded by objects.  In the classroom examples, people frequently did not extend the front of the room all way to the desks.  Second, people consider dynamics part of the context, in the safety example, people did not indicate that it was safe behind the lone turret in front of the others.

The connection between spatial regions and function has been explored in other robotics work, e.g. ~\cite{Karg:2012,Fasola:2013}, but these regions are based on fields anchored at single points in the environment or on a particular object. Therefore, they cannot account for the changes in context shown in this experiment which depend on multiple objects, agents, and simulation.

>>>>

%Recall from section \ref{} that in addition to being able to represent these regions for a single environment, the cognitive system (1) must recognize regions of the same type in new environments with new contexts, and (2) use the region for multiple reasoning tasks.  While spatial reasoning has been an active topic in AI and robotics for decades, CDSRs present a new problem which requires solutions beyond the current state-of-the-art. Regions are central to QSR work~\cite{Cohn:2001}. Regions can either have crisp boundaries, usually defined by geometric shapes (e.g. the bounding boxes of visually tracked objects~\cite{SridharCohn:10}), or vague boundaries created qualitatively by multiple crisp regions (e.g. the `egg-yolk model'~\cite{Cohn96b}), or by thresholding an underlying spatially-mapped function (e.g. those created by potential fields~\cite{brenneretal07ijcai} or by Gaussian kernels~\cite{burbridge-dearden12}). The fundamental decision when creating a computational model of a CDSR is the method used to represent its boundary. Given their context-dependent nature, boundary definitions based purely on single geometric shapes or a fixed number of points, seem unlikely to model the regions with sufficient accuracy.
%
%However, arbitrary boundaries can be defined using a sequence of geometric primitives (usually straight lines), as in chain codes for image region representations~\cite{Freeman:1961}. This is an approach we followed in previous work \cite{Hawes:2012}, where we defined CDSRs using \textit{anchor points} \cite{DBLP:journals/jetai/KlenkFTK11} as the vertices of the region polygon thereby linking the conceptual regions to perceived objects.   While satisfying the requirements of a cognitive systems solution, applying this model to our results of our experiemnt illustrates two limitations.  First, Regions are not always physically bounded by objects.  In the classroom examples, people frequently did not extend the front of the room all way to the desks.  Second, people consider dynamics part of the context, in the safety example, people did not indicate that it was safe behind the lone turret in front of the others.
%
%The connection between spatial regions and function has been explored in other robotics work, e.g. ~\cite{Karg:2012,Fasola:2013}, but these regions are based on fields anchored at single points in the environment or on a particular object. Therefore, they cannot account for the changes in context shown in this experiment which depend on multiple objects, agents, and simulation.

%JK Previous version above I replaced it with this shorter version below

Spatial reasoning has been an active topic in AI and robotics for decades, CDSRs present a new problem which requires solutions beyond the current state-of-the-art. Regions are central to QSR work~\cite{Cohn:2001} and also in the area of cognitive robitics (see \emph{inter alia.} ~\cite{brenneretal07ijcai,kelleher/costello:09}). A fundamental decision when creating a computational model of a CDSR is the method used to represent its boundary. Given their context-dependent nature, boundary definitions based purely on single geometric shapes or a fixed number of points, seem unlikely to model the regions with sufficient accuracy. However, arbitrary boundaries can be defined using a sequence of geometric primitives (usually straight lines). This is an approach we followed in previous work \cite{Hawes:2012}, where we defined CDSRs using \textit{anchor points} \cite{DBLP:journals/jetai/KlenkFTK11} as the vertices of the region polygon thereby linking the conceptual regions to perceived objects.  While satisfying the requirements of a cognitive systems solution, applying this model to our results of our experiemnt illustrates two limitations.  First, Regions are not always physically bounded by objects.  In the classroom examples, people frequently did not extend the front of the room all way to the desks.  Second, people consider dynamics part of the context, in the safety example, people did not indicate that it was safe behind the lone turret in front of the others. Finally, the connection between spatial regions and function has been explored in other robotics work, e.g. ~\cite{Karg:2012,Fasola:2013}, but these regions are based on fields anchored at single points in the environment or on a particular object. Therefore, they cannot account for the changes in context shown in this experiment which depend on multiple objects, agents, and simulation.

%--------------------------
